Integrated Management Model for Human Capital

### 2015-02-09 paper.tex
finish

\documentclass[12pt,a4paper,titlepage]{article}
%\usepackage[doublespacing]{setspace}
\usepackage[utf8]{inputenc}         %This is used for ASKII digits.
\usepackage{amsmath, amssymb}       %This is for mathematic statements,check"amath.colorado.edu/documentation/LaTex/Symbols.pdf"
\usepackage{amsfonts,mathrsfs}      %fonts~~
\usepackage{graphicx}               %This is for graph inserting.
\usepackage{paralist}               %Give me compact lists!!!!! 'compactitem' 'compactenum' 'compactdesc'
%\usepackage{bm}
\usepackage{caption2}                 %various kinds of bold texts.
\usepackage[top =2.54cm, bottom =2.54cm, left =3.18cm, right =3.18 cm]{geometry}
\usepackage{indentfirst}            %Indent the first letter
\usepackage{fancyhdr}               %Below is the head of the article.
\pagestyle{fancy}
\usepackage{booktabs}
\usepackage{lastpage}
\lhead{Team \# 33131}
\rhead{Page \thepage{} of \pageref{LastPage}}
\cfoot{}
%\numberwithin{equation}{section}    %Numbering of the equations will be based on sections.
%\usepackage{amsthm}
%\theoremstyle{definition}
%\newtheorem{def}{Definition}  %Below set the theorem system.
%\theoremstyle{plain}
%\newtheorem{thm}[law]{Thm}
%\theoremstyle{remark}
%\newtheorem*{remark}{Remark}
\newcommand{\boldit}[1]{\textbf{\textit{#1}}}
\usepackage{float}
\usepackage{paralist}
\usepackage{url}

@@

\title{Human Capital Model} \date{\today{}}
\maketitle

@@

Considering the shortage of the talent, it's essential for companys to
retain good people and make them well-trained. However, current
situation is not satisfactory while many talents always tend to get a
good job via job-hopping, causing orgnizational churn in employees who
are closely connected to them. In order to simulate this process and
improve it, we build a human capital model based on Social Network
Analysis and Markov process.

\subsection{Restatement of the Problem}
\label{sec:restatement-of-the-problem}

Problem C describe ICM as an orginaization of 370 people on human
capital. The company is facing some issues. ICM tend to make a
positive work atmosphere to gain the loyalty of an employee in their
early time.The churn of an some employee makes effect on productivity
and emotion on other employee. Lower quality employees often stay with
the company for a full career. The churn rate is 18\% per year and
mid-level positions suffer high  churn rate, even twice the average
rate of the rest of the company. HR prefer matching employees to the
right position. It only provides promotion opportunity for those who
have several years of work experience. ICM usually has only 85\% of
its 370 positions filled at any time and HR office is actively hiring
about 8\%-10\% of the ICM positions. The CEO salary is approximately
10 times the median of the salaries of all the employees, compared to
hundreds of times the median as found in many companies.

There are several tasks we need to finish according to our model:

\begin{itemize}
\item Build a Human Capital network model of ICM organization’s
  personnel situation.

\item Identify dynamic processes within the Human Capital network,
  which includes orginizatinal churn and direct and indirect effects on
  the organization’s productivity.

\item Analyze your organization’s budget requirements over the next 2
  years.

@@

\item Simulate the impact of 30\% churn in both junior managers and
  experienced supervisors, if other churn values remain at 18\%.It
  assumes that there is no external recruiting and ICM promote only
  qualified employees for the next two years.

\item Connect our Human Capital network to other organizational
  network layers such as information flow, trust, influence, and
  friendship that the other offices of ICM are considering building.
\end{itemize}

@@

\begin{itemize}
\item \textbf{assumption 1} If an employee has probability to
  promote, he won't churn.

@@

\item \textbf{assumption 2} For a vacancy,if there exists an
  employee measures up to it already, ICM won't recruit for it.

Since recruiting good people is difficult, time consuming and
expensive according to issue 5, it is wasteful to recruit for a
position if an employee can promote to it.

\item \textbf{assumption 3} Demotion won't occur.

\item \textbf{assumption 4} Administrative clerk won't promote or be
  transferred.

\item \textbf{assumption 5} Each division or office have at least one
  middle manager or senior manager.

@@

Most research for human capital can be classified as either
microscopic and macroscopic. Since either macroscopic or microscopic
methods are difficult to solve our problem perfectly, we approach the
problem with the combination of macroscopic and microscopic methods.

To measure the ability of each person, we use Quantitative Management
Performance. Via this measurement, we can classify differient kinds of
employees which will influence the promotion process.

To build the employee network and analyze its properties, we employ
the social network analysis (SNA) technique. In our case, the
employees are viewed as nodes and relationships as links among
them. So, We can simulate the complex relationship via this network.

Definitions of symbols employed in this section are listed in Table
\ref{variable1}:
\begin{table}
  \centering
  \begin{tabular}{l p{10cm}}
  \toprule{}
  Variable & Description \\
  \midrule{}
  $i$            &Index of an employee \\
  $L_{i,t}$          &The level of $i$ \\
  $s_{ij,t}$        &The relation strength from $i$ to $j$ \\
  $a_{ij,t}$        &Represent the influence caused by relationship
                    between superior and subordinate \\
  $f_{ij,t}$        &Represent the influence caused by relationship
                    between person with many friends and person with
                    few friends \\
  $c_{i,t}$        &Clustering Coefficient of $i$ \\ \bottomrule{}
\end{tabular}
\caption{Variables and Descriptions}\label{variable1}
\end{table}

\subsection{Human Performance Model}
\label{sec:human-model}

In this part, we buid a people model to evaluate an employee in four
aspects, in terms of \textbf{Quantitative Management Performance} ---
work achievement, work ability, work attitude and potential. These
four aspects are supposed to be quantized according to annual
evaluation based on performance as judged by the supervisor and we
take these independent variables as $A_{ac_i}$, $A_{ab_i}$, $A_{at_i}$
and $A_{po_i}$ for each employee $i$. For each of the four parameters,
it goes from 0 to 1. The statues are used for calculating the
probability that employee can promote. Meanwhile, they influence
leaving probability and team cohesiveness as well.

It is obvious that some of the parameters are somehow more important
than others. So in an effort to make our model more accurate and
reliable,we introduce a weighted index of deviation $AD_i$, with
\begin{equation}
  A_i=w_{ac} \cdot A_{ac_i} + w_{ab} \cdot A_{ab_i} + w_{at} \cdot A_{at_i} +
  w_{po} \cdot A_{po_i}
\end{equation}

@@

The meaning of the number in each cell is explained in Figure
\ref{important}. The numbers themselves are based on our own
subjective decisions.

\begin{table}[htb]
  \centering
  \begin{tabular}{cl}
    \toprule{}
    Intensity of Importance&Definition \\ \midrule{}
    1                      &Equal Importance \\
    2                      &Weak or slight \\
    3                      &Moderate importance \\
    4                      &Moderate plus \\
    5                      &Strong importance \\
    6                      &Strong plus \\
    7                      &Very strong or demonstrated importance \\
    8                      &Very, Very strong \\
    9                      &Extreme importance \\ \bottomrule{}
  \end{tabular}
  \caption{The fundamental scale of absolute numbers}\label{important}
\end{table}

We then get the weight of each factor by calculating the bigest
eigenvalue and it's corresponding eigenvector, as given in Table \ref{weight}.

\begin{table}
\begin{center}
\begin{tabular}{ccccc} \toprule{}
  Factor  &$A_{ac}$    &$A_{ab}$   &$A_{at}$    &$A_{po}$\\ \midrule{}
  Weight  &0.3805  &0.0709  &0.2371  &0.3030\\ \bottomrule{}
\end{tabular}
\end{center}
\caption{Weight for factors}\label{weight}
\end{table}

We test the consistency of the preferences for this instance of the
AHP.\@ For good consistency [Alonso and Lamata 2006, 446 - 447]:

@@

The social network model contains a directed weighted graph $G(V,E)$
in which $V$ denote the employees and $E$ denote the connection
between employees. Since there are personnel changes, $G(V,E)$ will
change with time goes by. In order to simulate this situation, we use
$G_t(V_t,E_t)$ instead of $G(V,E)$ where $t$ is a discrete
variable. So $G_t(V_t,E_t)$ denote the social network in the $t$-th
month.

First, we explain the way we build edges of $G_t(V_t,E_t)$.

When $t = 0$, there are about $370 \times 85\%$ nodes (employees) in
$G_t$. We build edges between employees in the same division or
office, since employees in the same division or office certainly know
each other. So each division or office form a complete graph and
employees in the differient division or office don't know others,
which is impossible. To solve this problem, we build 10 edges for each
employee with employees in other divisions with equal
probability. Then we build the other edges with probability
$p = \frac{\left|N_{i,t} \cap N_{j,t}\right|}{\left|N_{i,t} \cup
    N_{j,t}\right|}$
which is called Jaccard similarity coefficient[Jaccard 1901].

When $t > 0$, there will be employees leaving or joining the
company. If an employee leave, all his edges with other employees with
be deleted. If an employee newly join the company, he will follow
steps which employees at $t = 0$ take. This is the dynamic process of
graph $G_t(V_t,E_t)$.

Let $s_{ij,t}$ denote the weight from $i$ to $j$ at time $t$. We have
these properties of $G_t(V_t,E_t)$:

@@

  We made this graph directed and weighted because one person may
  consider another person his best friend while that person doesn't
  consider him a good friend. This situation may appear because of the
  relationship between superior and subordinate and the relationship
  between person with more friend and person with less friend. In
  general, $s_{ij,t} \ne s_{ij,t}$ for the reason above.

@@

  $a_{ij,t}$ denote the influence caused by the relationship between
  superior and subordinate, $f_{ij,t}$ denote the influence caused by
  the amount of friends for $i$ and $j$. We define
$$a_{ij,t}=\begin{cases}
  \frac{1}{2+\left|L_{i,t}-L_{j,t}\right|}, & L_{i,t} \ge L_{j,t} \\
  1-\frac{1}{2+\left|L_{i,t}-L_{j,t}\right|}, & L_{i,t} < L_{j,t} \\
\end{cases}$$
, where $L_{i,t}$ denote the level of $i$ at time $t$, and
$$f_{ij,t}=\frac{\left|N_{i,t} \cap
    N_{j,t}\right|}{\left|N_{i,t}\right|}$$.

@@

First, we explain the model of promotion aimed to predict the
promotion probability. We define the promotion rate of $i$ as
$p_i$ to evaluate the probability to promote. As a matter of fact, if
there is a vacancy, judging if an employee suits the site involves
work experience and ability. It is essential that he is supposed to
have several years of work experience according to issue 6. If an
employee satisfies the experience condition, it turns out to think
about his ability. Since in Human Performance Model, each employee's
ability is evaluated by a parameter $A_{D_i}$. For each level of
position, it has an ability standard, as shows in Table[]. The ability
of an employee are supposed to reach the four standard parameters
respectively, otherwise its $p_i$ is 0. For those who reach the
standard, the promotion probability can be calculated by the equation:
$p_i =\dfrac{A_{D_i}}{\sum_{\alpha} A_{D_\alpha}}$ where $\alpha$ represent
employee who have probability to promote.

According to assumption 1 and assumption 2, from $t$ to $t+1$, the
model update once according to the following rules:

\begin{itemize}
\item [\textit{step 1}] Promotion: If there's a vacancy in superior
  and $i$ has the ability to occupy this position, let $L_{i+1,t} =
  L_{i,t}+1$ with probability mentioned above and build edges between
  $i$ and his new colleagues.
\item [\textit{step 2}] Churn: If $i$ isn't promoted, he will have the
  probability to churn with a churn rate $l$.
\item [\textit{step 3}] Stay: If $i$ hasn't been promoted or churned,
  he will keep his job and do nothing.
\item [\textit{step 4}] Recruit: Recruit for vacancies when all the
  employees have done these 3 steps above.
\end{itemize}

@@

\begin{itemize}
\item \textbf{assumption 1} For the promotion probability and
  organization change, the other factors effects the churn probability
  is invariable.

Though churn derives from varieties of reasons and they are actually
lacking of known conditions and data to estimate them, we have to
regard it as stable in our model.
\end{itemize}

@@

The network of the company we've built changes in terms of
orgnizational churn and promotion. Considering various of factors in
reality, we build an orgnizational churn and promotion model to
predict the dynamic process.

The first part of the model is churn model.We define the churn rate of
an employee $i$ as $l_i$ to evaluate the probability to churn. $l_i$ is
usually controlled by sorts of factors to different degrees. We
divides $l_i$ into three parts:$l_{i1}$, $l_{i2}$ and$l_{i3}$.  $l_{i1}$
represents the churn rate because of lacking of promotion
opportunity. $l_{i2}$ represents the churn rate because of the changes
of other employees related to employee $i$. To simplify our model, we
presume that $l_i1$, $l_i2$ is linear correlated with $(1-p_i)$ and
$s_i$, which means

\begin{equation}
  l_{i1}=\lambda_1(1-p_i),l_{i2}=\lambda_2s_i
\end{equation}

$\lambda_1$ and $\lambda_2$ could be ensured in later calculation.

$l_{i3}$ represents the other factors we can't get any information from
the known conditons so that we regard it as stable.  Thus

\begin{equation}
  l_i = \lambda_1(1-p_i) + \lambda_2s_i +l_i3
\end{equation}

After analyzing a great deal of churn rate reports, we get the
composition of the three parts are 10.9\%, 2.2\% and 75.4\%
respectively. According to the percentage and the general
churn rate 18\%, we can calculate $\lambda_1$, $\lambda_2$ and
$l_{i3}$. As an orinigal condition,it satisfies

\begin{equation}
\label{lambda}
\begin{cases}
  \lambda_1 \sum_{i=1}^{370}(1-p_i) & =10.9\% \times 370 \times 1.5\% \\
  \lambda_2 \sum_{i=1}^{370}s_i & =2.2\% \times 370 \times 1.5\% \\
  l_{i3} & =1.5 \% \times 75.4 \%
\end{cases}
\end{equation}

Thus we can use Equation\ref{lambda} to calculate the churn rate $l_i$.

Analyzing the consequence of this phenomenon, we use our program to
simulate this process. As a result, we find a organizational churn in
our simulation as shown in Figure \ref{organizational-churn}.

@@

The black spots in the graph denote employees who have churned

@@

First, we explain the concept of clustering coefficient [Duncan
J. Watts and Steven Strogatz 1998] of $i$ denoted as $c_{i,t}$, which
is a measure of the degree to which nodes in a graph tend to cluster
together. $c_{i,t}$ is defined as:

$$c_{i,t}=\dfrac{\left| \left\{ s_{jk,t}:v_j,v_k \in M_i,s_{jk,t} \in E
    \right\} \right|}{k_{i,t}(k_{i,t}-1)}$$
where
$M_{i,t}=\left\{ v_j:s_{ij,t} \in E \and s_{ji,t} \in E \right\}$ and
$k_{i,t}=\left| N_{i,t} \right|$.

We assume that the company offers training programs for its employees monthly and newly hired employees start to get their salaries next month after they enter the company. With these two assumption, results can be drawn according to our model through simulation.

Budget can be divided into threee parts: salary budget, training budget and recruiting budget. The budget requirement predicted for next two years is listed in the table below in terms of $\sigma$.

\begin{tabular}{*{4}{c}}\toprule[2pt]
Total Budget & Salary Budget & Training Budget & Recruiting Budget\\ \midrule
1170.8$\sigma$ & 951.387$\sigma$ & 164.423$\sigma$ & 55.08$\sigma$ \\ \bottomrule[2pt]
\end{tabular}

To analyze the status of positions under different churn rate, we use
our model to simulate dynamic processes with these churn rate
constraints. We execute our program 100 times for each churn rate and
average the predicted values. Figure \ref{t4_p} shows the averaged
results our model predicted. Under all of these three conditions, the
number of employees in the company keeps rising. The higher the churn
rate, the lower the final full rate the company reaches after two
years. But ICM can sustain its 80\% for positions even if the churn
rate goes to 35\% according to our model's precition.

\begin{figure}[htb]
  \centering
  \includegraphics[width=10cm]{task4_r.pdf}\\
  \caption{Recruiting budget}\label{t4_r}
\end{figure}
\begin{figure}[htb]
  \centering
  \includegraphics[width=7cm]{task4_t.pdf}
  \includegraphics[width=7cm]{task4_s.pdf}\\
  \caption{Training budget and salary budget}\label{t4_t_s}
\end{figure}
The churn rate effect the budget of the company as well. The three
parts of the bugdet behave differently when churn rate increases. The
calculated budget is shown in Figure \ref{t4_r} and Figure
\ref{t4_t_s}. Each data point in three charts is an averaged result of
10 predictions and a linear trendline is added to each chart. It is
clear that recruiting budget showed in Figure \ref{t4_r} is likely to
be proportional to the churn rate while salary budget and training
budget showed in Figure \ref{t4_t_s} are likely to be inversely
proportional to the churn rate.

To maintain enough employees, the company has to spend more on
recruiting. So high turnover rate directly increase the recruiting
budget. High turnover rate's effect on training budget and salary
budget is more complex. On the one hand, when churn rate goes up,
vacancies in the middle level keeps rising due to long recruiting time
and low promote rate. On the other hand, the vacancies in lower level
remains low because of the short recruiting time. So the full rate of
the company decreases when churn rate rises. Since training budget and
salary budget are closely related to full rate, both of them decrease
when turnover rate goes up.

\begin{figure}[htb]
  \centering
  \includegraphics[width=10cm]{task5_p.pdf}\\
  \caption{Status of position}\label{t5_p}
\end{figure}
We apply following changes to our model to simulate the required process:\\
\begin{itemize}
\item Change the churn rate of junior managers and experienced supervisors to 30\%
\item Prohit external recruiting
\item Promoting only qualified employees
\end{itemize}
\begin{table}
        \begin{center}
                \begin{tabular}{l|cc}\toprule[2pt]
                \bfseries Level of Position & \bfseries Modified & \bfseries Original\\ \midrule
                Senior manager/Executive & 5.6 & 8.4\\
                Junior manager/Executive & 9.0 & 18.4\\
                Experienced supervisor & 7.4 & 23.0\\
                Inexperienced supervisor & 9.2 & 23.2\\
                Experienced employee & 72.6 & 107.4\\
                Inexperienced employee & 99.6 & 149.6\\
                Administrative clerk & 24.0 & 24.0\\ \bottomrule[2pt]
                \end{tabular}
                \caption{Status of position}\label{t5_p_t}
        \end{center}
\end{table}

>>>>

\documentclass[12pt,a4paper,titlepage]{article}
%\usepackage[doublespacing]{setspace}
\usepackage[utf8]{inputenc}         %This is used for ASKII digits.
\usepackage{amsmath, amssymb}       %This is for mathematic statements,check"amath.colorado.edu/documentation/LaTex/Symbols.pdf"
\usepackage{amsfonts,mathrsfs}      %fonts~~
\usepackage{graphicx}               %This is for graph inserting.
\usepackage{paralist}               %Give me compact lists!!!!! 'compactitem' 'compactenum' 'compactdesc'
%\usepackage{bm}
\usepackage{caption2}                 %various kinds of bold texts.
\usepackage[top =2.54cm, bottom =2.54cm, left =3.18cm, right =3.18 cm]{geometry}
\usepackage{indentfirst}            %Indent the first letter
\usepackage{fancyhdr}               %Below is the head of the article.
\pagestyle{fancy}
\usepackage{booktabs}
\usepackage{makecell}
\usepackage{lastpage}
\lhead{Team \# 33131}
\rhead{Page \thepage{} of \pageref{LastPage}}
\cfoot{}
%\numberwithin{equation}{section}    %Numbering of the equations will be based on sections.
%\usepackage{amsthm}
%\theoremstyle{definition}
%\newtheorem{def}{Definition}  %Below set the theorem system.
%\theoremstyle{plain}
%\newtheorem{thm}[law]{Thm}
%\theoremstyle{remark}
%\newtheorem*{remark}{Remark}
\newcommand{\boldit}[1]{\textbf{\textit{#1}}}
\usepackage{float}
\usepackage{paralist}
\usepackage{url}

@@

\title{Integrated Management Model for Human Capital}
\date{}
\maketitle

@@

Considering the shortage of the talent, it's essential for companys to
retain good people and make them well-trained. However, current
situation is not satisfactory while many talents always tend to get a
good job via job-hopping, causing orgnizational churn in employees who
are closely connected to them.

ICM is facing such an issue that the churn rate reachs 18\%. The churn rate of middle managers even reaches twice as much as others. At present, the company only has 85\% of its positions occupied while HR is recruiting only 8\%-10\% of the vacancies due to limited resources. In addition, HR department hopes to place employees to suitable positions to maximize their talent. In order to simulate this situation and help to improve it, we build a human capital model based on Social Network
Analysis and Markov process.

There are several tasks we need to accomplish:

\begin{itemize}
\item Build a Human Capital network model of ICM's personnel situation.

\item Identify dynamic processes within the Human Capital network,
  which includes organizatinal churn and direct and indirect effects on
  the organization's productivity.

\item Analyze the organization's budget requirements over the next 2
  years.

@@

\item Assumes that there is no external recruiting and ICM promotes
  only qualified employees for the next two years. Simulate the impact
  of 30\% churn rate in both junior managers and experienced
  supervisors, if other churn values remain 18\%.

\item Connect our Human Capital network to other organizational
  network layers such as information flow, trust, influence, and
  friendship that the other offices of ICM are considering building.
\end{itemize}
\section{Variables and Descriptions}

Definitions of symbols employed in this section are listed in \textbf{Table
\ref{variable1}}, where all the subscripts with $t$ represent the
$t$-th month and all the subscripts with $i$ represent the employee
indexed by $i$:

\begin{table}
  \centering
  \begin{tabular}{l p{10cm}}
  \toprule[2pt]
  Variable & Description \\
  \midrule{}
  $i$            &Index of an employee \\
  $L_{i,t}$          &The level of $i$ \\
  $A_{ac_i,t}$       &The work achievement of $i$ \\
  $A_{ab_i,t}$         &The work ability of $i$ \\
  $A_{at_i,t}$        &The work attitude of $i$ \\
  $A_{po_i,t}$       &The potential of $i$ \\
  $A_{i,t}$          &The grade of $i$ \\
  $s_{ij,t}$        &The relation strength from $i$ to $j$ \\
  $a_{ij,t}$        &The influence caused by leader-member relation
                    between $i$ and $j$ \\
  $f_{ij,t}$        &The influence caused by friendship
                    between $i$ and $j$\\
  $c_{i,t}$        &The Clustering Coefficient of $i$ \\
  $p_{i,t}$           &Promotion probability of $i$\\
  $l_{i,t}$          &Churn probability of $i$ \\
  $prod_{i,t}$       &Productivity of $i$ \\
  $salary_{i,t}$     &Salary of $i$ \\
  $d_{i,t}$          &The work experience of $i$ \\
  $m_{ij}$           &The variable to reflect whether employee indexed
                       by $i$ is suitable for position indexed by $j$
                       \\
  $B_{ac_j}$       &The suitable work achievement of position indexed
                     by  $j$ \\
  $B_{ab_j}$       &The suitable work ability of position indexed by
                     $j$ \\
  $B_{at_j}$       &The suitable work attitude of position indexed by
                     $j$ \\
  $B_{po_j}$       &The suitable potential of position indexed by $j$
                     \\
  $N$ & The number of employees over the next two years \\
$p$ & The average productivity over the next two years \\
$r$ & The percentage of recruiting positions in ICM positions \\
$c$ & The current churn rate \\
$ra$ & The ratio of the churn rate between middle managers and the
       rest employees \\
  \bottomrule[2pt]
\end{tabular}
\caption{Variables and Descriptions}\label{variable1}
\end{table}

@@

\begin{itemize}
\item \textbf{Assumption 1} If an employee has an opportunity to be promoted, he won't leave the company.

@@

\item \textbf{Assumption 2} For each vacancy, if there exists an
  employee satisfying its requirement, ICM won't recruit for it.

Since recruiting good people is difficult, time consuming and
expensive, it is wasteful to recruit for a
position if an employee satisfies the requirement.

\item \textbf{Assumption 3} Demotion won't occur.

\item \textbf{Assumption 4} Administrative clerk won't be promoted or be
  reassigned.

\item \textbf{Assumption 5} Each division or office has at least one
  middle manager or senior manager.

@@

Most researches on human capital can be classified as either
microscopic or macroscopic. Since both macroscopic and microscopic
methods alone can not solve the problem perfectly, we approach the
problem with the combination of macroscopic and microscopic methods.

To measure the ability of each person, we use Quantitative Management
Performance. Via this measurement, we can classify different kinds of
employees which will influence the promotion process.

To build the employee network and analyze its properties, we employ
the social network analysis (SNA) technique. In our model,
 employees are viewed as nodes and relationships are viewed as links 
 among employees. With this network, we can simulate the complex relationship.

\subsection{Employee Performance Model}
\label{sec:human-model}

In this part, we build an Employee Performance model to evaluate an employee in four
aspects, in terms of Quantitative Management Performance ---
work achievement, work ability, work attitude and potential\cite{3}. These
four aspects are supposed to be quantized according to the annual
evaluation based on performance judged by the supervisor and we
take these independent variables as $A_{ac_i,t}$, $A_{ab_i,t}$, $A_{at_i,t}$
and $A_{po_i,t}$ for each employee indexed by $i$. Each of these four parameters ranges from 0 to 1. They are used to calculate the
promotion probability for each employee. Meanwhile, they influence the
leaving probability and team cohesiveness.

It is obvious that these parameters are of different importance. So in an effort to make our model more accurate and reliable, we introduce a weighted index of deviation $A_{i,t}$, with
\begin{equation}
  A_{i,t}=w_{ac} \cdot A_{ac_i,t} + w_{ab} \cdot A_{ab_i,t} + w_{at} \cdot A_{at_i,t} +
  w_{po} \cdot A_{po_i,t}
\end{equation}

@@

The meaning of the number in each cell is explained in \textbf{Figure
\ref{important}}\cite{11}. The numbers themselves are based on our own
subjective decisions.

\begin{table}[htb]
  \centering
  \begin{tabular}{cl}
    \toprule[2pt]
    Intensity of Importance & Definition \\ \midrule{}
    &\\
    1 & Equal Importance \\
    2 & Weak or slight \\
    3 & Moderate importance \\
    4 & Moderate plus \\
    5 & Strong importance \\
    6 & Strong plus \\
    7 & Very strong or demonstrated importance \\
    8 & Very, Very strong \\
    9 & Extreme importance \\ \bottomrule[2pt]
  \end{tabular}
  \caption{The fundamental scale of absolute numbers}\label{important}
\end{table}

We then get the weight of each parameter by calculating the bigest
eigenvalue and it's corresponding eigenvector, as given in \textbf{Table \ref{weight}}.

\begin{table}
\begin{center}
\begin{tabular}{ccccc} \toprule[2pt]
  Factor  &$A_{ac}$    &$A_{ab}$   &$A_{at}$    &$A_{po}$\\ \midrule{}
  Weight  &0.3805  &0.0709  &0.2371  &0.3030\\ \bottomrule[2pt]
\end{tabular}
\end{center}
\caption{Weight for factors}\label{weight}
\end{table}

We test the consistency of the preferences for this instance of the
AHP.\@ For good consistency \cite{4}:

@@

The social network model contains a directed weighted graph $G(V,E)$
in which $V$ denotes the employees and $E$ denotes the connection
between employees. Since there are personnel changes, $G(V,E)$ will
change with time goes by. In order to simulate this situation, we use
$G_t(V_t,E_t)$ instead of $G(V,E)$ where $t$ is a discrete
variable. So $G_t(V_t,E_t)$ denote the social network in the $t$-th
month.

Firstly, we explain the way we build edges of $G_t(V_t,E_t)$.

When $t = 0$, there are about $370 \times 85\%$ nodes (employees) in
$G_t$. We build edges between employees in the same division or
office, since employees in the same division or office certainly know
each other. So each division or office form a complete graph. To establish inter-division or inter-office relations, we build 10 edges for each
employee with employees in other divisions with equal
probability. Then we build the other edges between employee indexed by
$i$ and employee indexed by $j$ with the probability
$p = \frac{\left|N_{i,t} \cap N_{j,t}\right|}{\left|N_{i,t} \cup
    N_{j,t}\right|}$
which is called Jaccard similarity coefficient[Jaccard 1901].

When $t > 0$, there will be employees leaving or joining the
company. If an employee leaves, all his relations with other employees will
be deleted. If an employee newly joins the company, he will follow
steps which employees at $t = 0$ take.

Let $s_{ij,t}\in E_t$ denotes the weight from $i$ to $j$ in $t$-th
month. We have these properties of $G_t(V_t,E_t)$:

@@

  We made this graph directed and weighted because one person may
  consider another person his best friend while that person doesn't
  consider him a good friend. This situation may appear in leader-member relations and the relations between person with more friend and person with less friend. In
  general, $s_{ij,t} \ne s_{ij,t}$ for the reason above.

@@

  $a_{ij,t}$ denotes the influence caused by leader-member relation
  between the employee indexed by $i$ and the employee indexed by $j$,
  $f_{ij,t}$ denotes the influence calculated by the amount of friends
  of the employee indexed by $i$ and the employee indexed by $j$. We define

\begin{equation}
a_{ij,t}=\begin{cases}
  \frac{1}{2+\left|L_{i,t}-L_{j,t}\right|}, & L_{i,t} \ge L_{j,t} \\
  1-\frac{1}{2+\left|L_{i,t}-L_{j,t}\right|}, & L_{i,t} < L_{j,t} \\
\end{cases}
\end{equation}

, where $L_{i,t}$ denotes the level of $i$ in $t$-th month, and

\begin{equation}
f_{ij,t}=\frac{\left|N_{i,t} \cap
    N_{j,t}\right|}{\left|N_{i,t}\right|}
\end{equation}

@@

Firstly, we explain the model of promotion designed to predict the
promotion probability. The promotion rate of the employee indexed by $i$ is defined as
$p_i$ to evaluate the probability of promotion. If
there is a vacancy, judging if an employee is qualified for the
position depends on his work experience and ability. First of all, it
is essential to evaluate whether he has the special work
experience. If he matches the condition of work experience, his
ability will be evaluated subsequently. In Human Performance Model,
each employee's
ability is evaluated by a parameter $A_{D_i}$. Each level of
position has its own ability standard. The ability
of an employee is supposed to reach the four standard parameters
respectively, otherwise its $p_i$ is set to 0. For those who reach the
standard, the promotion probability can be calculated by the equation:
$p_i =\dfrac{A_{D_i}}{\sum_{\alpha} A_{D_\alpha}}$ where $\alpha$ represents
employee who has probability to be promoted.

According to \textbf{Assumption 1} and \textbf{Assumption 2}, the
model updates monthly (from $t$ to $t+1$) obeying the following rules:

\begin{itemize}
\item [\textit{step 1}] Promotion: If there's a superior vacancy
  and the employee indexed by $i$ satisfies the requirement of the
  position, let $L_{i+1,t} =
  L_{i,t}+1$ with the probability mentioned above and build edges
  between   $i$ and his new colleagues.
\item [\textit{step 2}] Churn: If the employee indexed by $i$ isn't promoted, he will have the
  probability to churn with a churn rate $l_{i,t}$.
\item [\textit{step 3}] Stay: If the employee indexed by $i$ hasn't been promoted or churned,
  he will be kept on his original position.
\end{itemize}

@@

\begin{itemize}
\item \textbf{Assumption 6} Except the promotion probability and
  organization change, the other factors effects the churn probability
  are invariable.

Though churn probability is influenced by varieties of factors, we do not  have enough information about these factors. Therefore, we have to
regard most of them as constants in our model.

\item \textbf{Assumption 7} Productivity of the company is the sum of the productivity of all employees.

@@

The network of the company we've built changes from time to time due to
organizational churn and promotion. Considering various of factors in
reality, we build an organizational churn and promotion model to
predict the dynamic process.

The first part of the model is churn model. We define the churn rate of
the employee indexed by $i$ as $l_{i,t}$. We divides $l_{i,t}$ into three
parts: $l_{i1,t}$, $l_{i2,t}$ and $l_{i3,t}$.  $l_{i1,t}$
represents the churn rate resulting from the lack of promotion
opportunity. $l_{i2,t}$ represents the churn rate resulting from the personnel alterations of other employees who share an edge with employee indexed by $i$. To simplify our model, we
presume that $l_{i1,t}$, $l_{i2,t}$ is linear correlated with $(1-p_{i,t})$ and
$s_{ij,t}$, which means

\begin{equation}
  l_{i1,t}=\lambda_1(1-p_{i,t}),l_{i2,t}=\lambda_2\sum_{j}s_{ij,t}
\end{equation}

$\lambda_1$ and $\lambda_2$ could be determined in later calculation.

$l_{i3,t}$ represents the other factors we regard as constants, about which we can't get enough information from the known conditons.  Thus

\begin{equation}
l_{i,t}=\lambda_1(1-p_{i,t}) + \lambda_2 \sum_{j} s_{ij,t} + l_{i3,t}
\end{equation}

After analyzing a great deal of churn rate reports, we define the
coefficients of the three parts to 10.9\%, 2.2\% and 75.4\%
respectively\cite{1}\cite{2}. With these percentages and the general
churn rate 18\%, we can calculate $\lambda_1$, $\lambda_2$ and
$l_{i3,t}$. As an original condition, it satisfies

\begin{equation}
\label{lambda}
\begin{cases}
  \lambda_1 \sum_{i=1}^{370}(1-p_{i,t}) & =10.9\% \times 370 \times 1.5\% \\
  \lambda_2 \sum_{i=1}^{370}\sum_{j}s_{ij,t} & =2.2\% \times 370 \times 1.5\% \\
  l_{i3} & =1.5 \% \times 75.4 \%
\end{cases}
\end{equation}

Thus we can use \textbf{Equation \ref{lambda}} to calculate the churn rate $l_i$.

To analyze the consequence of this phenomenon, we used our program to
simulate this process. As a result, we observed an organizational churn in
our simulation as shown in \textbf{Figure \ref{organizational-churn}}.

@@

The black spots in the graph denote employees who have leaved during
the past year. Each graph represents the status of 3 months after the
privious graph. In the first 3 months, there is only one employee leaving the company. In the second 3 months, there are two employees leaving the
company, while 4 more employees leave during the next 3 months. As a
conclusion, there's a phenomenon of organizational churn according to
our model.

@@

Firstly, we explain the concept of clustering coefficient [Duncan
J. Watts and Steven Strogatz 1998] of employee indexed by $i$ denoted as $c_{i,t}$, which
is a measure of the degree to which nodes in a graph tend to cluster
together. $c_{i,t}$ is defined as:

\begin{equation}
c_{i,t}=\dfrac{\left| \left\{ s_{jk,t}:v_j,v_k \in M_i,s_{jk,t} \in E
    \right\} \right|}{k_{i,t}(k_{i,t}-1)}
\end{equation}

where
$M_{i,t}=\left\{ v_j:s_{ij,t} \in E \and s_{ji,t} \in E \right\}$ and
$k_{i,t}=\left| N_{i,t} \right|$.

In order to get the definition of productivity, we give some factors
that will influence productivity:

\begin{itemize}
\item The first factor is churn rate which will reduce the
  productivity if churn rate is at a high level.
\item The second factor is the clustering coefficient $c_{i,t}$,
  which determines team cohesiveness. We consider that the higher
  $c_{i,t}$ is, the higher the productivity is.
\item The third factor is the ability of employee indexed by $i$ mentioned in
  \textbf{Section \ref{sec:human-model}}. It is obvious that a higher ability
  brings a higher productivity.
\item The fourth factor is the time duration that
  $i$ stays in his position, denoted as $d_{i,t}$. Productivity will increase as the employee get familiar with his job.
\item The last factor is the salary of employee indexed by $i$, denoed as
  $salary_{i,t}$. It is obvious that salary will influence the productivity.
\end{itemize}

According to the factors described above, we have the formula for calculating productivity:

\begin{equation}
  prod_{i,t}=salary_{i,t} \cdot c_{i,t} \cdot A_{i,t} \cdot d_{i,t} \cdot (1-l_{i,t})
\end{equation}

Finally, we introduce the direct and indirect effects on the
organization's productivity. With the relation updates, edges in our
employee network update, which causes the clustering coefficient
changes. Meanwhile, the salary and work experience will change over
time, which results in the changing of productivity. These factors
effect the productivity collectively.

\section{Further Improved Model}

As the HR manager faces many problems such as identifying employees that
are likely to churn and maximizing employees' knowledge and
abilities, we propose our further improved model to help the HR managers.
